Practice Problems

### 2023-09-21 Stats Rethinking/Ch7/Practice Problems.qmd
Finished through medium

@@

# 7M4

What happens to the effective nymber of parameters, as measured by PSIS or WAIC, as a prior becomes more concentrated? Why? Perform some experiments, if you are not sure.

@@

>>>>

$$
AIC=-2*LLPD+2p\\
WAIC(y,\Theta)=-2(LLPD-\sum var_{\theta}logp(y_i|\theta))
$$

Of these information criterion WAIC is more general. In order to transform WAIC into AIC you need the following conditions:

1.  The priors are flat or overwhelmed by the likelihood.
2.  The posterior distribution is approximately multivariate Gaussian.
3.  The sample size $N$ is much greater than the number of parameters $k$.

@@

Is this a trick question? It's obvious that if models are fit to different training data then they are different models entirely and not just variations on assumptions.

# 7M4\*

What happens to the effective number of parameters, as measured by PSIS or WAIC, as a prior becomes more concentrated? Why? Perform some experiments, if you are not sure.

Shouldn't it become smaller? Since as you get more data they will drown out the noise of overfitting created by the extra parameters.

@@

In 2007, *The Wall Street Journal* published an editorial with a graph
